---
title: "Peer Assessment 1 - Reproducible Research"
author: "R. Ballard"
date: "October 17, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coursera - Reproducible Research Project 1

This is the markdown file for the first peer review project for Reproducible Research. Course 5 in the Data Science Specialization. The below code chuck will read in the raw data for the project. This data frame consists of:
- Three Columns
 1.  Year
 2.  Steps
 3.  Interval
- 17568 observations


```{r dataread}
setwd("C:/Users/rballard/Desktop/Personal/Data Science Certification/repres/RepData_PeerAssessment1")

activity <- read.csv(file="activity.csv")
activity$date<-as.Date(activity$date,format="%Y-%m-%d")
activity$interval<-as.factor(activity$interval)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
